Dragonfly Territory Ananlysis

### 2020-11-23 analysis/analysisSS.Rmd
working on analysis

coenigrion <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Coenagrion puella')
ischnura <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Ischnura elegans')
lestes <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Lestes sponsa')
libellula <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Libellula quadrimaculata')
sympetrum <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Sympetrum striolatum')

@@

par(mfrow=c(2,3))
plot(ischnura$YEAR, ischnura$ABUNDANCE)
plot(coenigrion$YEAR, coenigrion$ABUNDANCE)
plot(lestes$YEAR, lestes$ABUNDANCE)
plot(libellula$YEAR, libellula$ABUNDANCE)
plot(sympetrum$YEAR, sympetrum$ABUNDANCE)

@@

ischnuraAY <- getAbundanceYear(ischnura)
coenigrionAY <- getAbundanceYear(coenigrion)
lestesAY <- getAbundanceYear(lestes)
libellulaAY <- getAbundanceYear(libellula)
sympetrumAY <- getAbundanceYear(sympetrum)

@@

coenigronCompAY <- rbind(row1959, row1960, row1961, row1962, coenigrionAY)
ischnuraCompAY <- rbind(row1959, row1960, row1961, ischnuraAY)
lestesCompAY <- rbind(row1959, row1960, row1961, row1962, row1963, lestesAY)
# libellula will be dealt with differently because it is missing rows within the dataframe
sympetrumCompAY <- rbind(row1959, row1960, row1961, sympetrumAY)

prelibellulaCompAY <- rbind(row1960, row1972, row1974, libellulaAY)
# this will add the rows I want, but now in chronological order
libellulaCompAY <- dplyr::arrange(prelibellulaCompAY, YEAR)

# there are species missing from this, they need to be added separately

brachytronAbundance <- c(0,0,0,0,0,0,0,0,0,1,0,0,2,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
pyrrhosomaAbundance <- c(0,0,3,20,18,5,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
aeshnaAbundance <- c(0,0,0,0,1,2,3,1,1,2,3,1,5,1,2,0,0,0,1,1,1,0,2,1,1,3,1,2,2,2)

>>>>

cPuella <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Coenagrion puella')
iElegans <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Ischnura elegans')
lSponsa <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Lestes sponsa')
lQuadrimaculata <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Libellula quadrimaculata')
sStriolatum <- dplyr::filter(rawDragonfly, GENUS_SPECIES == 'Sympetrum striolatum')

@@

par(mfrow=c(2,3))
plot(iElegans$YEAR, iElegans$ABUNDANCE)
plot(cPuella$YEAR, cPuella$ABUNDANCE)
plot(lSponsa$YEAR, lSponsa$ABUNDANCE)
plot(lQuadrimaculata$YEAR, lQuadrimaculata$ABUNDANCE)
plot(sStriolatum$YEAR, sStriolatum$ABUNDANCE)

@@

iElegansAY <- getAbundanceYear(iElegans)
cPuellaAY <- getAbundanceYear(cPuella)
lSponsaAY <- getAbundanceYear(lSponsa)
lQuadrimaculataAY <- getAbundanceYear(lQuadrimaculata)
sStriolatumAY <- getAbundanceYear(sStriolatum)

# I want to rename the abundance column with species name to aid comparison and readibility

iEleganSAY <- dplyr::rename(iElegansAY, iElegans_abundance = ABUNDANCE)
cPuellaSAY <- 
lSponsaSAY <- 
lQuadrimaculataSAY <- 
sStriolatumSAY <-

@@

cPuellaCompAY <- rbind(row1959, row1960, row1961, row1962, cPuellaSAY)
iElegansCompAY <- rbind(row1959, row1960, row1961, iElegansSAY)
lSponsaCompAY <- rbind(row1959, row1960, row1961, row1962, row1963, lSponsaSAY)
# lQuadrimaculata will be dealt with differently because it is missing rows within the dataframe
sStriolatumCompAY <- rbind(row1959, row1960, row1961, sStriolatumSAY)

prelibellulaCompAY <- rbind(row1960, row1972, row1974, lQuadrimaculataSAY)
# this will add the rows I want, but now in chronological order
lQuadrimaculataCompAY <- dplyr::arrange(prelibellulaCompAY, YEAR)

# there are species missing from this dataset, they need to be added separately, I will source (and cite) the abundance data
# also need a vector corresponding to the years

dragonflyYears <- c(1959:1988)

bPratenseAbundance <- c(0,0,0,0,0,0,0,0,0,1,0,0,2,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
pNymphulaAbundance <- c(0,0,3,20,18,5,1,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0,0)
aCyaneaAbundance <- c(0,0,0,0,1,2,3,1,1,2,3,1,5,1,2,0,0,0,1,1,1,0,2,1,1,3,1,2,2,2)
sSanguineumAbundance <- c(0,0,0,0,0,1,0,0,1,0,2,0,1,0,0,1,0,1,4, 11, 3, 0, 1, 9, 6, 10, 4, 9, 3, 4)
aGrandisAbundance <- c(0,0,0,0,0,0,0,4,0,1,1,0,2,0,2,0,0,0,1,1,0,1,2,1,0,1,1,4,0,1)

bPratenseCompAY <- data.frame(bPratenseAbundance, dragonflyYears)
pNymphulaCompAY <- data.frame(pNymphulaAbundance, dragonflyYears)
aCyaneaCompAY <- data.frame(aCyaneaAbundance, dragonflyYears)
sSanguineumCompAY <- data.frame(sSanguineumAbundance, dragonflyYears)
aGrandisCompAY <- data.frame(aGrandisAbundance, dragonflyYears)
